GSS Education Analysis (Working Title)

### 2023-03-14 outputs/paper/paper.qmd
fix graphs
add variables table

#### Load Library ####
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(modelsummary)

@@

#### Ordering Highest Year of Education Achieved ####

cleaned_gss_2021$educ <- 
  factor(cleaned_gss_2021$educ, 
         levels = c("8th Grade", "9th Grade", "10th Grade", "11th Grade", "12th Grade", "1 Year of College", "2 Years of College", "3 Years of College", "4 Years of College", "5 Years of College", "6 Years of College", "7 Years of College", "8 Years of College"))

```{r}
#| echo: false
#| warning: false
#| label: fig-1
#| fig-cap: "Respondent's Sex by Highest Year of Education Achieved"

#### Creating Graph to Compare Sex Against Year of Completed Education ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(x = sex, fill = educ)) +
  geom_bar() + 
  theme_classic() +
  labs(x = "Sex",
       y = "Number",
       fill = "Highest Year of Education Completed")+
  theme(legend.key.size = unit(1,"line"))

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```
```{r}
#| echo: false
#| warning: false
#| label: fig-9
#| fig-cap: "rich work vs class"

@@

>>>>

#### Load Library ####
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(modelsummary)
library(kableExtra)
library(knitr)

@@

#### Create Variable Description Tibble ####

 variable_table <-
  tibble(
    "Variable" = c(
      "class",
      "degree",
      "finrela",
      "happy",
      "satjob",
      "satfin",
      "sex"
    ),
    "Variable Description" = c(
      "Self-ascribed class of the respondent",
      "Highest level of education achieved by respondent",
      "Self-ascribed ranking of respondnet when compared to other US households",
      "Respondent's rating of how happy they are daily",
      "Level of satisfaction with the work respondents do",
      "Level of satisfaction with the job respondents have",
      "Sex of the respondent"
    )
  )
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-1
#| tbl-cap: "Variable Descriptions"

#### Add Variable Table ####
variable_table |>
  kable(booktabs = TRUE) |>
  kable_styling(font_size = 7, latex_options = "hold_position")

@@

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = class)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Highest Level of Education",
       x = "Number",
       fill = "Self-Ascribed Class")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-9
#| fig-cap: "rich work vs class"

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-20
#| fig-cap: "happy vs degree"

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = degree, fill = happy)) +
  geom_bar() +
  theme_classic() +
  labs(y = "degree",
       x = "number")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```
